Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-13 docs/ms.tex
no psfig
Update ms.tex

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}

@@

\section{XXX}
\label{sec:XXX}

@@

\section{XXX}
\label{sec:XXX}

@@

\section{XXX}
\label{sec:XXX}

>>>>

% Packages:
% \input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}

@@

\section{method}
\label{sec:XXX}

\subsection{Likelihood Functions}
If we know the ellipticity distribution of unlensed galaxies based
on some parasmeters $\alpha$,the likelihood of reduced shear $g$
and parameter $\alpha$ is like:

\begin{equation}
L(\vec{g},\alpha|\epsilon_{\ell})=p(\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
\end{equation}

Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$are complex numbers.So
$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
determinant term.Here the prior distribtuion we use for $\vec{g}$
is a 2Dflat distribution in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
1 & |\vec{g}|<1\\
0 & |\vec{g}|>1
\end{cases}$

The prior of $\alpha$ some how depends on the model we choose for
intrinsic ellipticity distribution .When we use the step function
model for P($\epsilon_{0}$),we find that we need to use a prior on
$\alpha$ .
\begin{equation}
Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

Given the likehood functions and priors we can also calculated the
marginalized likelihood function.
\begin{equation}
p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha
\end{equation}

Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
just $Prior(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
\begin{equation}
p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)Prior(\vec{\alpha}|\xi)d\alpha
\end{equation}

\subsection{model for P($\epsilon_{0}$)}
Two flexible models are tested for P($\epsilon_{0}$)
One is Beta function model and one is step function model.
While using step function model we use a prior regularzation on $\alpha$ 
\begin{equation}
Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

\subsection{MCMC Sampler}

While making the posterior samples we choose to use the classical Gibbs sampler.

@@

\section{Result}
\label{sec:XXX}

\subsection{Posterior samples}
We show the posterior samples of both g and $\alpha$ ,for both beta function and step function model.
\subsection{Bias Test}
We test the systematical bias of our estimator.
We plot $g_{1}-g_{1}^{true}$ VS $g_{1}^{true}$ ,and put on an error bar which equals standard deviation of 
marginalized likehood functon $p(Data|g_{1})$ ,and use a linear fit to determin the m,c value and their standard 
deviations.

\subsection{Accuracy Test}
We compare the mean square error of our estimator with average and the estimator that could be constructed if the true unlensed
ellipticity distribution were known.
We show how the mean square error varies with number of galaxies ,number of patches and so on.

\subsection{Accuracy Test}
We show some example how our method works when there is an Gaussian noise added on the observed $\epsilon$

\subsection{prefactor $\xi$}
Discuss about how $\xi$ is tuned ,the danger if $\xi$ is set to be too large or too small.

@@

\section{Discussion}
\label{sec:XXX}
